Argennon: A Scalable Cloud Based Smart Contract Platform Using Argument of Knowledge Systems

### 2023-02-05 tex/sections/apm.tex
Add a section about simplifying zk components
Signed-off-by: aybehrouz <behrouz_ayati@yahoo.com>

@@

>>>>

\section{Introduction}\label{sec:introduction3}

@@

\section{Simplifying Complex Components}\label{sec:simplifying-complex-components}

Assume that we have a complex component which has a considerable arithmetic circuit complexity. If this component
is needed in some arbitrary computation steps, we will need to repeat its circuit in every step of the computation. This
will increase the complexity of proof generation considerably. Fortunately, there is a workaround and instead of
repeating the circuit of the component, we can use a simpler cryptographic accumulator circuit during the
computation, and use a final verification circuit at the end to verify the functionality of the component.

Every component accepts an input $in$ and produces an output $out$. As a result we can denote the component by a
deterministic function that maps an input sequence with any arbitrary length $k$, to an output sequence with the same
length:
\[
    f((in_1,in_2,\dots,in_k)) \coloneqq (out_1,out_2,\dots,out_k)
\]
In every step of the computation, we replace this component with a cryptographic accumulator which receives $in$ and
$out$ as its inputs and gets activated in the same computation steps that the component must be active. When the
accumulator is active, it accumulates its inputs, so at the end of the computation it has computed a digest:
\[
    h(in_1,out_1,in_2,out_2,\dots,in_k,out_k) \coloneqq digest_f
\]
where $k$ is the number of steps that our component must have been active.

Now the prover needs to prove that he knows values $in_1,out_1,\dots,in_k,out_k$ such that they are correctly
produced by the component:
\[
    f((in_1,\dots,in_k)) = (out_1,\dots,out_k)
\]
and their digest is also correct:
\[
    h(in_1,out_1,\dots,in_k,out_k) = digest_f
\]
where $f$ and $digest_f$ are known to the prover and verifier.

The circuit for verifying this assessment usually is straight forward. When the computation involves a large
number of steps and the component is complex, this approach can reduce the cost of proof generation considerably. Memory
components are good candidates for being simplified by this method.

Interestingly, this approach can reduce the number of computation steps. When we use an accumulator circuit instead
of the component, $out$ can be available in the same computation step that $in$ is available. This will
eliminate the computation step that is needed for generating $out$ by the component's circuit.
